{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-22 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

                beyond Nesterov's rule"

@@

            The following papers are related to stabiling, improving the acceleration scheme without monotone restarting. 

@@

    \begin{lemma}[Proximal gradient envelope] 

@@

>>>>

                beyond Nesterov's rule". 

@@

            The following papers are related to stabilizing, improving the acceleration scheme without monotone restarting. 

@@

    \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}

@@

        The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
        \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
